Quantifying and Modeling Global Water Accessibility including Water Typology

### 2021-01-20 docs/manuscript/manuscript.tex
Explanation of Figure 5 and Figure 6.

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{transportation-time}
  \caption{Advanced Correlation Graph of Modes of Transportation and Time}
  \label{fig:year}
\end{figure}

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width=.7\textwidth]{transportation-time}
  \caption{Advanced Correlation Graph of Modes of Transportation and Time}
  \label{fig:year}
\end{figure}
Figure 5 shows that Households possessing a motorcycle (mcyc) has a positive correlation with Households using a tube well/borehole (bore) and Households using rainwater (rain) with a p-value of less than 0.01. Similar to the previous analysis, there is a relationship between a mode of transportation to retrieve potential water sources. Figure 6 also shows that households possessing an animal-drawn cart (acar) have a positive and strong relationship with households using unprotected well water (uwel) with a p-value of less than 0.001. The results demonstrate that different modes of transportation factor into the accessibility of retrieving water sources on a global scale, therefore, there should be consideration of these variables to increase access to improved water sources.

% The results demonstrate that when a threshold of 30 minutes is used, 1% to 27% of the population of these 17 countries would be considered as not having access to improved water sources.
